Ceph Parallel File System Evaluation Report

### 2013-09-20 conclusion.tex
Brad's attempt to cut to 5 pages
So here is most of my attempt to cut this paper to 5 pages.
I amde it to about 5.7 pages.  I could go after it some more,
but this is a good first draft point to check and see if we need
to add back anything I took out.

I also added the IEEEabbrv.bib file since I couldn't build
without it.

Ceph is built on the assumption that the underlying hardware components are
unreliable, with little or no redundancy and failure detection capability.
This assumption is not valid for high-end HPC centers like OLCF. We have
disabled replication for pools, haven't measured and quantified processing
overhead, and we do not know yet if this would be significant. Investigating
this remains as a future work.

Ceph performs \textbf{metadata + data} journaling, which is fine for host
systems that have locally attached disks. However, this presents a problem in
DDN SFA10K-like hardware, where the backend LUNs are exposed as block devices
through IB over SRP protocol. The journaling write requires twice the
bandwidth compared to Lustre-like meta data-only journaling mechanism. For
Ceph to be viable in large-scale capability HPC environments like OLCF,
journaling operations need further design and more engineering efforts.

In our earlier tests, we experienced large performance swings during different
runs, low read performance when transfer size is small, and I/O errors tend to
happen when system is under stress (more clients and large transfer sizes).
However, with systematic performance engineering and development efforts, we
have seen a steady improvement through different releases. As of now, Ceph
system on our testbed is able to perform close to 80\% of raw hardware
capability at RADOS level and close to 70\% at file system level (after
accounting for journaling overheads) . This is still no comparison to Lustre
yet, but by no means a small feat for such a \textit{young} technology. It is,
in fact, a very respectable level of performance.

>>>>

%Ceph is built on the assumption that the underlying hardware components are
%unreliable, with little or no redundancy and failure detection capability.
%This assumption is not valid for high-end HPC centers like OLCF. We have
%disabled replication for pools, haven't measured and quantified processing
%overhead, and we do not know yet if this would be significant. Investigating
%this remains as a future work. 
In our early tests, we experienced large performance swings during different
runs, low read performance when transfer size is small, and I/O errors tend to
happen when system is under stress (more clients and large transfer sizes).
However, with systematic performance engineering and development efforts, we
have seen a steady improvement through different releases. As of now, the Ceph
system on our testbed is able to perform close to 80\% of raw hardware
capability at RADOS level and close to 70\% at file system level (after
accounting for journaling overheads) . 
%This is still no comparison to Lustre
%yet, but by no means a small feat for such a \textit{young} technology. It is,
%in fact, a very respectable level of performance.

Ceph is built on the assumption that the underlying hardware components are
unreliable, with little or no redundancy and failure detection capability.
This assumption is not valid for high-end HPC centers like OLCF.
Ceph performs \textbf{metadata + data} journaling, which is appropriate for host
systems that have locally attached disks rather than DDN SFA10K-like hardware,
where the backend LUNs are exposed as block devices through IB over SRP
protocol. The journaling write requires twice the bandwidth compared to
Lustre-like meta data-only journaling mechanism. For Ceph to be viable in
large-scale capability HPC environments like OLCF, journaling operations need
to support HPC storage hardware.

### 2013-09-20 testbed.tex
Brad's attempt to cut to 5 pages
So here is most of my attempt to cut this paper to 5 pages.
I amde it to about 5.7 pages.  I could go after it some more,
but this is a good first draft point to check and see if we need
to add back anything I took out.

I also added the IEEEabbrv.bib file since I couldn't build
without it.

In the following discussion, we use ``servers'', ``osd servers'', ``server
hosts'' interchangeably. We will emphasize with ``client'' prefix when we want
to distinguish it from above.  All hosts  (client and servers) were configured
with Redhat 6.3 and kernel version 3.5.1 initially, and later upgraded to 3.9,
Glibc 2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and
0.55 release in the initial tests, upgraded to 0.64 and then to 0.67RC for a
final round of tests.

@@

Our testing methodology is bottom to top. We start our evaluation from the
lowest level (i.e. block-level)  to establish a baseline performance and work
our way up to the top (i.e. file system-level). We establish an expected
theoretical performance of a given hardware or software layer and then compare
that with the observed results of our experiments. Each added new layer to the
stack introduces new bottlenecks and re-defines the expected theoretical
performance of the overall system. We will explain each component or layer and
its expected performance before we present our observed results.

Our tools for benchmarking and evaluating different layers also change as we
go up in the stack.  For example, a tool perfect for assessing block-level
performance over a single server host might be completely inadequate for
observing parallel file system performance over multiple clients. As we
present our evaluations, we will also introduce and explain our benchmark
tools along the way.

>>>>

%In the following discussion, we use ``servers'', ``osd servers'', ``server
%hosts'' interchangeably. We will emphasize with ``client'' prefix when we want
%to distinguish it from above.  
All hosts  (client and servers) were configured
with Redhat 6.3 and kernel version 3.5.1 initially, and later upgraded to 3.9,
Glibc 2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and
0.55 release in the initial tests, upgraded to 0.64 and then to 0.67RC for a
final round of tests.

@@

%Our testing methodology is bottom to top. We start our evaluation from the
%lowest level (i.e. block-level)  to establish a baseline performance and work
%our way up to the top (i.e. file system-level). We establish an expected
%theoretical performance of a given hardware or software layer and then compare
%that with the observed results of our experiments. Each added new layer to the
%stack introduces new bottlenecks and re-defines the expected theoretical
%performance of the overall system. We will explain each component or layer and
%its expected performance before we present our observed results.

%Our tools for benchmarking and evaluating different layers also change as we
%go up in the stack.  For example, a tool perfect for assessing block-level
%performance over a single server host might be completely inadequate for
%observing parallel file system performance over multiple clients. As we
%present our evaluations, we will also introduce and explain our benchmark
%tools along the way.
